\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}

The rapid growth of e-commerce platforms has made competitive monitoring increasingly difficult for small sellers and individual analysts. This thesis designs and implements an Amazon Marketplace Intelligence Tracker for scheduled monitoring of three consumer-electronics categories: Gaming Keyboards, True Wireless Earbuds, and Portable Chargers. The project is framed as an operational thesis prototype rather than a low-latency commercial intelligence platform.

The implemented system uses Apify as the sole Amazon data source and Supabase PostgreSQL as the warehouse. Daily category ingestion collects Top-50 ranking snapshots, while watchlist ingestion tracks product-level signals such as price, Best Seller Rank, stock status, listing content, and image fingerprints for selected ASINs. Weekly review ingestion adds customer-review text and Amazon-provided aspect summaries. The analytics pipeline is orchestrated through Python scripts and GitHub Actions, with database access centralized through the repository's Supabase wrapper.

Nine analytical modules are implemented: entrant and exit detection, listing and image-change detection using perceptual hashing, sponsored share-of-voice estimation, K-Means price-tier segmentation, RoBERTa sentiment analysis, Listing Quality Score (LQS), Brand Momentum Score (BMS), Prophet-based seven-day price forecasting, and a rule-based alert engine. The outputs are consumed through two delivery surfaces: pull-based Streamlit and web dashboards, and push-based Telegram briefs generated by three OpenClaw agents. The agents access the warehouse through thirteen read-only Python skills, keeping conversational delivery separate from data mutation.

The 13-day pilot window from April 17 to April 29, 2026 produced 1,756 category-ranking rows, 409 daily product snapshots, and 3,986 raw review records. The sentiment evaluation covered 3,851 reviews using star ratings as a noisy distant-supervision proxy. RoBERTa achieved 81.17\% accuracy and a macro-$F_1$ score of 0.594, with strong positive-class performance ($F_1 = 0.908$), useful negative-class recall (0.782), and weak neutral-class performance ($F_1 = 0.158$). The forecast evaluation covered all 30 watchlist ASINs under a three-day holdout using a five-way model comparison: naive carry-forward, linear trend (OLS), Exponential Smoothing (ETS), ARIMA(1,1,0), and Prophet. The naive baseline achieved the lowest pooled MAE (\$1.292), with ARIMA the closest alternative (\$1.323). Prophet ranked fifth (MAE \$2.970, MAPE 6.75\%), yet is retained in the deployed system for its calibrated 80\% prediction intervals (empirical coverage 67.8\%), which the Momentum Strategist agent uses as a volatility signal rather than a precise point forecast. The results confirm that Amazon prices approximate a random walk over short horizons, and forecast accuracy is expected to improve as data accumulates beyond 30 days.

Operationally, the system generated 1,060 entrant/exit events and 1,248 alerts, including 55 high-severity alerts. It also identified high-momentum ASINs through BMS and showed that LQS was generally saturated among the tracked watchlist, with an average score of 93.4 out of 100. No image-change event exceeded the configured pHash threshold during the observed window, so image-change detection is reported as an implemented capability rather than a frequent empirical finding.

The thesis contributes an integrated, code-backed framework that connects scheduled Amazon data ingestion, reproducible analytical metrics, dashboard exploration, and read-only tool-using Telegram agents. The result is a low-cost market-intelligence prototype that can support daily and weekly monitoring workflows while making its empirical limitations explicit.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Amazon marketplace, competitive intelligence, Apify, Supabase, K-Means clustering, RoBERTa sentiment, Prophet forecasting, perceptual hashing, distant supervision, Listing Quality Score, Brand Momentum Score, OpenClaw, tool-using agents, Telegram delivery.
