\chapter*{ACKNOWLEDGEMENTS}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

The completion of this thesis would not have been possible without the
guidance, support, and encouragement of many individuals and
institutions. I would like to express my sincere gratitude to all those
who contributed, directly or indirectly, to the development of this
research.

First and foremost, I am deeply grateful to my supervisor,
\textbf{Dr.\ Nguyen Manh The}, for his patient guidance, constructive
feedback, and continuous encouragement throughout the research process.
His advice helped me refine the scope of the study, strengthen the
methodological foundation, and present the engineering implementation
in a more rigorous academic form. His emphasis on defensible evidence,
careful evaluation, and clear technical reasoning has had a lasting
influence on the way I approach applied data science projects.

I would also like to express my appreciation to the Faculty of
Mathematical Economics at the National Economics University, and
especially to the lecturers of the Data Science in Economics and
Business (DSEB 64) programme. The knowledge and training I received in
statistics, econometrics, machine learning, data engineering, and
software development provided the essential foundation for this thesis.
The interdisciplinary nature of the programme encouraged me to treat
data collection, modelling, evaluation, and deployment as an integrated
analytical workflow rather than as isolated technical components.

I am also thankful to the open-source and developer communities whose
tools supported the implementation of this project, including
\texttt{scikit-learn}, Hugging Face Transformers, Facebook Prophet,
\texttt{imagehash}, Supabase, Streamlit, Plotly, and the OpenClaw
runtime. These technologies made it possible to build and validate a
working market-intelligence system within the practical constraints of
an undergraduate thesis.

Finally, I would like to thank my family and friends for their
understanding, patience, and encouragement during the process of
developing the system, analysing the results, and writing this thesis.
Their support gave me the motivation to complete the work with
persistence and care.

\vspace{1cm}
\begin{flushright}
  \textit{Hanoi, May 2026}\\
  \textbf{Nguyen Thi Mai Linh}
\end{flushright}
