\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}

The rapid growth of e-commerce platforms has created unprecedented
opportunities for data-driven competitive intelligence. This thesis
designs and implements an end-to-end automated pipeline for monitoring
and analysing the Amazon consumer-electronics marketplace, focusing on
three high-competition categories: Gaming Keyboards, True Wireless
Earbuds, and Portable Chargers.

The system collects daily Top-50 category rankings, product-level metrics
(Best Seller Rank, price, stock status, Buy Box ownership), and customer
reviews for 30 watchlist ASINs over a 13-day collection window using the
Apify cloud scraper and a Supabase PostgreSQL warehouse. Image-change
detection is performed via 64-bit perceptual hashing (pHash) with a
Hamming-distance threshold of 10 bits, and listing content changes are
tracked via field-level fingerprinting.

Six analytical modules are developed: (1) a K-Means price-tier model that
segments products into entry, mid-range, and premium clusters; (2) a
Listing Quality Score (LQS) composite metric over seven content
sub-components; (3) a Brand Momentum Score (BMS) combining BSR velocity,
review velocity, and sentiment; (4) a RoBERTa-based sentiment pipeline at
the review and aspect levels; (5) a Facebook Prophet 7-day price-trend
forecaster with 80\% prediction intervals; and (6) a rule-based alert
engine. The two predictive components are evaluated under defensible
protocols --- distant supervision against star ratings for sentiment, and
walk-forward backtesting with a naive last-value baseline for price
forecasting.

Results from the 13-day pilot deployment show RoBERTa achieving 81.2\%
accuracy and 0.594 macro-F\textsubscript{1} on 3{,}851 distantly-labelled
reviews (positive F\textsubscript{1} 0.908, negative 0.715, neutral 0.158);
Prophet matching but not exceeding the naive last-value MAE of \$0.601
(MAPE 1.16\%, 80\% PI coverage 90.2\%) on a 3-day hold-out across 17
ASINs; the rule-based engine surfacing 1{,}248 alerts of which 55 are
high-severity; and 1{,}060 entrant/exit events of which 99 involve Top-10
positions.

Beyond the analytics, the thesis introduces a multi-agent delivery layer
built on the OpenClaw runtime: three specialist Telegram bots
(Competitor Spy, Sentiment Detective, Momentum Strategist) call thirteen
read-only Python skills against the Supabase warehouse and produce
production-grade briefs both interactively and on a daily / weekly cron
schedule. Together with an interactive Streamlit dashboard, this delivers
the same intelligence in two complementary modalities --- pull
(dashboard) and push (Telegram).

\vspace{0.5cm}
\noindent\textbf{Keywords:} Amazon marketplace, competitive intelligence,
web scraping, price tiering, K-Means clustering, RoBERTa sentiment,
Prophet forecasting, perceptual hashing, multi-agent LLM, Telegram delivery.
